### 2018-11-14 paper.tex
began work on paper

\documentclass[10pt]{article}
% We could also do
% \documentclass[10pt, twoside]{article}
% which shifts everything slightly to the
% side which makes it easier to read if
% it's all stapled together. 
\usepackage[doublespacing]{setspace}
\usepackage{mathtools}
\usepackage{array}
\usepackage{booktabs}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{xcolor}
\graphicspath{{.}}
\title{Optimizing the Robotics Closet}
\author{Sasha Krassovsky, John Lim, Andrey Ryabtsev}
\begin{document}
\maketitle
\pagebreak

\section{Introduction}
The Husky Robotics team is a team of both undergraduate and graduate students
from UW building a Mars rover to compete in the University Rover Challenge.
The rover must perform a variety of tasks, such as autonomous navigation, soil
collection, and typing on a keyboard with a robotic arm. The team is divided
into subsystems: Chassis, Arm, Science, Electronics, Software, and Manufacturing.
The subsystems work independently but collaborate to create the robot. Given
all these tasks and the relatively short amount of time given to build out the
functionality, efficiency is key when it comes to the build process.
\par
The robotics team has only a small closet in the Mechanical Engineering Building.
The closet stores the robot along with all of the tools, electronics, sheet metal,
carbon fiber, and plastics that go into building the robot. Each item belongs to
one of the subsystems, and is usually stored near other items belonging to that
subsystem. Unfortunately, the robotics closet is not particularly organized, and
members often spend on the order of 10 minutes looking for the thing they needed.
Our goal is to find a reorganization plan for the items in the closet such that
expected duration of each closet visit is minimized and items belonging to the
same subsystem are in the same connected component on the shelves.
\par
The closet has two shelves, one on each side. One side stores items in
uniformly-sized boxes while the other side has several other classes of items,
such as soldering irons, and boxes of various sizes. The rover is stored in
the middle of the room on a big cart. Behind it is the robotic arm and the
science station. In the back are the sheet metal, various metallic cylinders,
wood, and rolls of carbon fiber. By examining the frequencies of retrieval
by each team and treating the closet as a grid, we should be able to produce
a better layout of the closet.

\begin{center}
  \includegraphics[scale=0.15]{closet.jpg} \\
  The robotics closet before optimization. 
\end{center}

\section{Related Work}
Deepesh Singh's \emph{A Beginner’s guide to Shelf Space Optimization using Linear Programming}
explains an integer programming formulation for finding the optimal layout of a store
that maximizes sales. The guide organizes the store into several racks, each with
a certain number of shelves. One key assumption is that only one product can fit
on a rack. The model uses a table showing how many sales are generated by each item
depending on which rack it is placed. The objective function is then the profit
generated by a given arrangement. Arrangements are represented by a matrix, with
each $a_{ij}$ representing whether product $j$ is on shelf $i$. If it is, the
$a_{ij}$ is $1$ and $0$ otherwise. The guide shows how to maximize this profit function.
Although this approach is a good start, our problem differs in several ways: we can
fit more than one box on each shelf, and our goal is to minimize time of retrieval
rather than maximize profits.

\textbf{\color{red} TODO: More related work}

\section{Model}

\end{document}

### 2018-11-14 solver.py

@@ -39,3 +39,4 @@ for line in f:
     })
 f.close()
 
+m = Model()

### 2018-11-15 paper.tex
other stuff

@@
 
+\section{Assumptions}
+Most items in the robotics closet are in boxes. As a result, we assume that all
+items are rectangular prisms. Although items such as the chemicals or soldering irons
+are not strictly rectangle-shaped, it would be strange for another item reached into
+the empty areas of the items' bounding boxes. Taking advantage of this, we approximate
+all items as being rectangular prisms, and measure their bounding boxes.
+\par
 \section{Model}

### 2018-11-15 solver.py
optimization

@@ -11,14 +11,15 @@ subs = {
 }
 
 f = open('Robotics Closet Inventory - Sheet1.tsv', 'r')
-parts = []
+items = []
 for line in f:
     substrs = line.split('\t')
     dims = [float(x) for x in substrs[1].split('x')]
     prob = float(substrs[-1])
-    parts.append({
+    area = min(dims[0], dims[1]) * dims[2]
+    items.append({
         'name' : substrs[0],
-        'dims' : dims,
+        'area' : area,
         'prob' : prob,
         'sub'  : subs[substrs[2]]
     })
@@ -31,12 +32,51 @@ for line in f:
     dist = int(substrs[0])
     dims = [float(x) for x in substrs[1].split('x')]
     component = int(substrs[2])
-    
+    area = dims[0] * dims[1]
     shelves.append({
         'dist' : dist,
-        'dims' : dims,
+        'area' : area,
         'comp' : component
     })
 f.close()
 
 m = Model()
+
+# Create decision variable matrix
+decisions = []
+for shelf in shelves:
+    decisions.append([])
+    for item in items:
+        decisions[-1].append(m.addVar(vtype=GRB.BINARY))
+
+assert len(decisions) == len(shelves)
+
+# Area constraints per shelf
+for i in range(len(decisions)):
+    assert len(decisions[i]) == len(items)
+    shelf_area_expr = decisions[i][0] * items[0]['area']    
+    for j in range(len(decisions[i]) - 1):
+        shelf_area_expr = shelf_area_expr + decisions[i][j + 1] * items[j + 1]['area']
+    m.addConstr(shelf_area_expr <= shelves[i]['area'])
+
+# Items can only go into one spot
+for i in range(len(items)):
+    constr = decisions[0][i]
+    for j in range(len(shelves) - 1):
+        constr = constr + decisions[j + 1][i]
+    m.addConstr(constr == 1)
+
+# Items from the same subsystem must be in the same connected component
+for sub in range(len(subs)):
+    item_indices = [i for i in range(len(items)) if items[i]['sub'] == sub]
+    for component in range(3):
+        shelf_indices = [i for i in range(len(shelves)) if shelves[i]['comp'] == component]
+        expr = sum(sum([decisions[j][i] for j in shelf_indices]) for i in item_indices)
+        m.addConstr(expr == [0, len(item_indices)])
+
+# Objective Function
[…]

### 2018-11-15 solver.py
IT WORKS

@@ -49,6 +49,12 @@ for shelf in shelves:
     for item in items:
         decisions[-1].append(m.addVar(vtype=GRB.BINARY))
 
+connected_comp_decisions = []
+for i in range(3):
+    connected_comp_decisions.append([])
+    for j in range(len(subs)):
+        connected_comp_decisions[-1].append(m.addVar(vtype=GRB.BINARY))
+        
 assert len(decisions) == len(shelves)
 
 # Area constraints per shelf
@@ -66,17 +72,28 @@ for i in range(len(items)):
         constr = constr + decisions[j + 1][i]
     m.addConstr(constr == 1)
 
+# A subsystem can only go into one connected component
+for sub in range(len(subs)):
+    expr = sum([x[sub] for x in connected_comp_decisions])
+    m.addConstr(expr == 1)
+
 # Items from the same subsystem must be in the same connected component
 for sub in range(len(subs)):
     item_indices = [i for i in range(len(items)) if items[i]['sub'] == sub]
     for component in range(3):
         shelf_indices = [i for i in range(len(shelves)) if shelves[i]['comp'] == component]
-        expr = sum(sum([decisions[j][i] for j in shelf_indices]) for i in item_indices)
-        m.addConstr(expr == [0, len(item_indices)])
+        expr = sum([sum([decisions[j][i] for j in shelf_indices]) for i in item_indices])
+        m.addConstr(expr == (len(item_indices) * connected_comp_decisions[component][sub]))
 
 # Objective Function
-obj = sum(sum([shelf['dist'] / item['prob'] for item in items]) for shelf in shelves)
+obj = sum(sum([shelves[j]['dist'] * items[i]['prob'] * decisions[j][i] for i in range(len(items))]) for j in range(len(shelves)))
 m.setObjective(obj, GRB.MINIMIZE)
 
 m.update()
 m.optimize()
+
+for shelf in range(len(shelves)):
+    print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf]['comp'], shelves[shelf]['dist']))
+    names = [items[x]['name'] for x in range(len(decisions[shelf])) if decisions[shelf][x].X > 0]
+    for item in names:
+        print('\t' + item)

### 2018-11-15 paper.tex
wrote up model

@@
 \graphicspath{{.}}
+\newtheoremstyle{named}{}{}{}{}{\bfseries}{.}{.5em}{\thmnote{#3}}
+\theoremstyle{named}
+\newtheorem*{nthm}{Theorem}
 \title{Optimizing the Robotics Closet}
@@
 the middle of the room on a big cart. Behind it is the robotic arm and the
-science station. In the back are the sheet metal, various metallic cylinders,
+vscience station. In the back are the sheet metal, various metallic cylinders,
 wood, and rolls of carbon fiber. By examining the frequencies of retrieval
@@
 \par
+\textbf{\color{red} TODO: Fill in the rest of the assumptions}
+
 \section{Model}
+We collected data from the robotics closet by measuring each item and shelf. Each
+shelf $s$ is represented as an ordered triple $(d, a, c)$, where $d$ is the
+distance from the door in ``shelf-lengths'', $a$ is the area of the shelf, and
+$c$ is the connected components to which the self belongs.
+\par
+Each item is represented with an ordered triple $(a, p, s)$, where $a$ is the area
+of the item, $p$ is the probability that the item is selected, and $s$ is the item's
+subsystem. Notice that we represent each item as a 2-dimensional area. This is valid
+because we assumed that each shelf had a single unit of depth. As a preprocessing step,
+we choose to minimize the area. However, we cannot rotate always the item into a
+horizontal orientation. Therefore, $h$ is constant. For an item $i$ with length $l_i$,
+width $w_i$, and height $h_i$, its area $a_i$ is given by 
+$$a_i = \min(l_i, w_i) \cdot h_i$$
+\par
+Let there be $n$ shelves and $m$ items, $k$ subsystems, and $l$ is the number of
+connected components. Our decision variables lie in two matrices
+$$W = (w_{ij}), 1 \leq i \leq n, 1 \leq j \leq m$$
+$$C = (c_{ij}), 1 \leq i \leq l, 1 \leq j \leq k$$
+Each $w_{ij}$ and $c_{ij}$ is a binary variable, i.e. each $w_{ij}, c_{ij} \in {0, 1}$.
+Each $w_{ij}$ is $0$ if item $j$ is not on shelf $i$ and $1$ otherwise. $c_{ij}$ is
+$1$ if subsystem $j$ lies in connected component $i$ and $0$ otherwise. 
+$C$ is a $l \times k$ matrix because there are l connected components and k subsystems. \\
+Note about notation: $a^i_k$ indicates the area of item $k$ while $a^s_k$ indicates the
+area of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
+$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 
+\par
+The model is subject to the following constraints:
+\begin{enumerate}
+\item $\sum_{j = 1}^{m}w_{ij}a^i_j \leq w^s_i, 1 \leq i \leq n$.
+\item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
+\item $\sum_{j = 1}^{l}c_{ji} = 1, 1 \leq i \leq k$.
+\item Let $K$ be the set of indices of items belonging to subsystem $i$. Let
+  Let $L$ be the set of indices of shelves belonging to connected component $j$.
+  Then $\sum_{a \in K}\sum_{b \in L}w_{ba} = |K| \cdot c_{ji}, 1 \leq i \leq k, 1 \leq j \leq l$.
+\end{enumerate}
+Since each probability $p$ is less than 1, we incentivize putting items with higher probability
+in the front by multiplying the probability by the distance. Thus, our objective function
+becomes
+$$\min z = \sum_{i = 1}^{n}\sum_{j = 1}^{m} d_j p_i w_{ij}$$
+
+\textbf{Explanation of Constraints:}
+\begin{enumerate}
+\item The sum of all of the items on a given shelf must be less than or equal to
+  the maximum area that the shelf can support. We multiply by $w_{ji}$ so that
+  items not included on the shelf are not counted.
+\item Each column of $W$ can only have one $1$, because we cannot put an item
+  on two shelves simultaneously. Since each row represents a shelf, we simply
+  traverse the whole column and ensure its sum is exactly $1$. Notice that if
+  we had put $\leq 1$, the constraint would have been invalid because then
+  no items would have been included. Thus, this constraint implicitly enforces
+  the constraint that every item be included.
+\item Each column of $C$ can only have one $1$ because all items belonging to
+  a subsystem must be in the same connected component, and therefore a subsystem
+  can be in exactly one connected component. Similarly to constraint 2, summing
+  this and ensuring that the sum is 1 enforces the idea that every subsystem is
+  included.
+\item The intuition behind this constraint is that either all items belonging
+  to a subsystem are in the same connected component, or none are. Thus, we
+  use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not.
+\end{enumerate}
 

### 2018-11-15 solver.py

@@ -26,7 +26,7 @@ for line in f:
 f.close()
 
 shelves = []
-f = open('shelfdim.tsv')
+f = open('shelfdim.tsv', 'r')
 for line in f:
     substrs = line.split('\t')
     dist = int(substrs[0])

### 2018-11-16 paper.tex
w0w rip metal boi closet

@@
 \par
+We also assumed that certain parts of the robotics closet are not to be moved.
+For example, the shelf containing aluminum brackets and blocks for machining was excluded from the model entirely.
+This is due to the cumbersome nature of moving hundreds of unboxed chunks of metal, and due to opposition to its transportation by team members who frequently use it.
+The food pantry portion as well as some non-food items that made their way into it was similarly excluded after brief deliberation.
+Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since
 \textbf{\color{red} TODO: Fill in the rest of the assumptions}

### 2018-11-16 paper.tex
more assumptions (depth and some items unmoved)

@@
 The food pantry portion as well as some non-food items that made their way into it was similarly excluded after brief deliberation.
-Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since
-\textbf{\color{red} TODO: Fill in the rest of the assumptions}
+Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since the access to other closets is unaffected by the contents of these.
+\par
+Another simplifying assumption we made is that all drawers have one unit of depth.
+In other words, we cannot insert items one behind another.
+This is a valid assumption to make because having to pull an item from behind another would drastically reduce the retrieval time of both items, undoing much of the benefits of our optimization.
+This can be adjusted to be a soft constraint (penalize heavily for items that are one behind another) if the model is infeasible without this change.
+In the meantime, we are reasonably confident that disallowing multiple units of depth is the best approach keeping in mind our ultimate goal of convenience.
 

### 2018-11-16 paper.tex
add some sections, write some stuff in the sections

@@
 
+\section{Solution and Results}
+We used the Gurobi optimization library to solve the formulated integer programming problem.
+The results placed 11 items into Shelf 5, 16 items into Shelf 6, 13 items into Shelf 7, 13 items into Shelf 8, 11 items into Shelf 9, 2 into 10, 1 into 11, 2 into 12, and 11 into 13.
+The remaining shelves had no items placed in them.
+This confirmed our intuition that there was plenty of space for the items even with the single depth layer constraint.
+A brief examination of the items allocated to each specific shelf provides support for validity of the model; it is not difficult to imagine the items listed placed compactly, but plausibly.
+\par
+Only the shelves that have distance 2 (highest distance in the input data set) are left empty.
+This is an indication that proximity is, in fact, taken into account by the model.
+Finally, LiPo batteries are placed onto the same drawer, as are NVIDIA Jetsons and other closely related items.
+This validates that the connected components constraint is being considered.
+
+\section{Improvements}
+We noticed that the model packed together very many items while leaving four perfectly good shelves empty.
+Especially when considering that there are items we likely forgot to catalogue, as well as items that would get added later on, we may consider adding space remaining in shelves as a soft constraint.
+This could be done by either reducing the width of each shelf or by padding the items on all sides to imply that there must be room between each item.
+This would also have the added benefit of making items easier to take out, since it is illogicall to stuff some shelves to the last inch while leaving whole drawers to collect dust.
+
+\section{Conclusions}
+
+\section{Acknowledgements}
+
 \end{document}

### 2018-11-16 paper.tex
add buncha shit idk like the bs at the end and shit fuck

@@
 \section{Conclusions}
+In conclusion, we are happy to have found an integer programming approach with the aforementioned constraints and objective function to be successful at finding a reasonably optimal arrangement of items.
+We were able to learn the practical challenges of solving a real-world linear programming problem, whilst still getting a result that has legitemate applications.
 
 \section{Acknowledgements}
+We would like to thank:
+- Dr. Sara Billey for providing us with guidance throughout the project,
+- Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
+- UW Husky Robotics for providing the closet to undergo optimization,
+- Nolan Donovan for working with us to understand and solve this problem.
 

### 2018-11-16 paper.tex
formatting and spelling fix

@@
 \section{Solution and Results}
-We used the Gurobi optimization library to solve the formulated integer programming problem.
-The results placed 11 items into Shelf 5, 16 items into Shelf 6, 13 items into Shelf 7, 13 items into Shelf 8, 11 items into Shelf 9, 2 into 10, 1 into 11, 2 into 12, and 11 into 13.
-The remaining shelves had no items placed in them.
-This confirmed our intuition that there was plenty of space for the items even with the single depth layer constraint.
-A brief examination of the items allocated to each specific shelf provides support for validity of the model; it is not difficult to imagine the items listed placed compactly, but plausibly.
+We used the Gurobi optimization library to solve the formulated integer programming
+problem. The results placed 11 items into Shelf 5, 16 items into Shelf 6, 13 items
+into Shelf 7, 13 items into Shelf 8, 11 items into Shelf 9, 2 into 10, 1 into 11,
+2 into 12, and 11 into 13. The remaining shelves had no items placed in them.
+This confirmed our intuition that there was plenty of space for the items
+even with the single depth layer constraint. A brief examination of the items
+allocated to each specific shelf provides support for validity of the model;
+it is not difficult to imagine the items listed placed compactly, but plausibly.
 \par
-Only the shelves that have distance 2 (highest distance in the input data set) are left empty.
-This is an indication that proximity is, in fact, taken into account by the model.
-Finally, LiPo batteries are placed onto the same drawer, as are NVIDIA Jetsons and other closely related items.
-This validates that the connected components constraint is being considered.
+Only the shelves that have distance 2 (highest distance in the input data set)
+are left empty. This is an indication that proximity is, in fact, taken into
+account by the model. Finally, LiPo batteries are placed onto the same drawer,
+as are NVIDIA Jetsons and other closely related items. This validates that the
+connected components constraint is being considered.
 
 \section{Improvements}
-We noticed that the model packed together very many items while leaving four perfectly good shelves empty.
-Especially when considering that there are items we likely forgot to catalogue, as well as items that would get added later on, we may consider adding space remaining in shelves as a soft constraint.
-This could be done by either reducing the width of each shelf or by padding the items on all sides to imply that there must be room between each item.
-This would also have the added benefit of making items easier to take out, since it is illogicall to stuff some shelves to the last inch while leaving whole drawers to collect dust.
+We noticed that the model packed together very many items while leaving four
+perfectly good shelves empty. Especially when considering that there are items
+we likely forgot to catalogue, as well as items that would get added later on,
+we may consider adding space remaining in shelves as a soft constraint. This
+could be done by either reducing the width of each shelf or by padding the
+items on all sides to imply that there must be room between each item. This
+would also have the added benefit of making items easier to take out, since
+it is illogical to stuff some shelves to the last inch while leaving whole
+drawers to collect dust.
 
 \section{Conclusions}
-In conclusion, we are happy to have found an integer programming approach with the aforementioned constraints and objective function to be successful at finding a reasonably optimal arrangement of items.
-We were able to learn the practical challenges of solving a real-world linear programming problem, whilst still getting a result that has legitemate applications.
+In conclusion, we are happy to have found an integer programming approach
+with the aforementioned constraints and objective function to be successful
+at finding a reasonably optimal arrangement of items. We were able to learn
+the practical challenges of solving a real-world linear programming problem,
+whilst still getting a result that has legitemate applications.
 
@@
 We would like to thank:
-- Dr. Sara Billey for providing us with guidance throughout the project,
-- Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
-- UW Husky Robotics for providing the closet to undergo optimization,
-- Nolan Donovan for working with us to understand and solve this problem.
-
+\begin{itemize}
+\item Dr. Sara Billey for providing us with guidance throughout the project,
+\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
+\item UW Husky Robotics for providing the closet to undergo optimization,
+\item Nolan Donovan for working with us to understand and solve this problem.
+\end{itemize}
 \end{document}

### 2018-11-16 paper.tex
references

@@
 Deepesh Singh's \emph{A Beginner’s guide to Shelf Space Optimization using Linear Programming}
-explains an integer programming formulation for finding the optimal layout of a store
-that maximizes sales. The guide organizes the store into several racks, each with
-a certain number of shelves. One key assumption is that only one product can fit
+\cite{india} explains an integer programming formulation for finding the optimal layout
+of a store that maximizes sales. The guide organizes the store into several racks, each
+with a certain number of shelves. One key assumption is that only one product can fit
 on a rack. The model uses a table showing how many sales are generated by each item
@@
 \item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
-\item UW Husky Robotics for providing the closet to undergo optimization,
+\item Husky Robotics for providing the closet to undergo optimization,
 \item Nolan Donovan for working with us to understand and solve this problem.
 \end{itemize}
+
+\section{References}
+\begin{thebibliography}{9}
+\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
+  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
+  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
+\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
+  Linear Programming.” Analytics Vidhya, 2016
+\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
+  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
+  Informatica e Sistemistica, University of Bologna, 2001
+\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
+  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
+\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
+  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
+\end{thebibliography}
 \end{document}

### 2018-11-30 solver.py
attempt to make it be 1D

@@ -16,10 +16,10 @@ for line in f:
     substrs = line.split('\t')
     dims = [float(x) for x in substrs[1].split('x')]
     prob = float(substrs[-1])
-    area = min(dims[0], dims[1]) * dims[2]
+    horizontal = min(dims[0], dims[1])
     items.append({
         'name' : substrs[0],
-        'area' : area,
+        'horizontal' : horizontal,
         'prob' : prob,
         'sub'  : subs[substrs[2]]
     })
@@ -32,10 +32,10 @@ for line in f:
     dist = int(substrs[0])
     dims = [float(x) for x in substrs[1].split('x')]
     component = int(substrs[2])
-    area = dims[0] * dims[1]
+    horizontal = dims[0] * dims[1]
     shelves.append({
         'dist' : dist,
-        'area' : area,
+        'horizontal' : horizontal,
         'comp' : component
     })
 f.close()
@@ -60,10 +60,10 @@ assert len(decisions) == len(shelves)
 # Area constraints per shelf
 for i in range(len(decisions)):
     assert len(decisions[i]) == len(items)
-    shelf_area_expr = decisions[i][0] * items[0]['area']    
+    shelf_length_expr = decisions[i][0] * items[0]['horizontal']    
     for j in range(len(decisions[i]) - 1):
-        shelf_area_expr = shelf_area_expr + decisions[i][j + 1] * items[j + 1]['area']
-    m.addConstr(shelf_area_expr <= shelves[i]['area'])
+        shelf_length_expr += decisions[i][j + 1] * items[j + 1]['horizontal']
+    m.addConstr(shelf_length_expr <= shelves[i]['horizontal'])
 
 # Items can only go into one spot
 for i in range(len(items)):

### 2018-11-30 visualizer/js.js

@@ -1,5 +1,8 @@
 window.onload = ()=>{
 	let c = document.getElementById("c"), g = c.getContext("2d");
 	g.fillStyle = "black";
-	g.fillRect(0, 100, 200, 200);
+	
+	const SHELVES = [
+		{width: 12, height: 8}
+	];
 }

### 2018-11-30 solver.py
L

@@ -32,7 +32,7 @@ for line in f:
     dist = int(substrs[0])
     dims = [float(x) for x in substrs[1].split('x')]
     component = int(substrs[2])
-    horizontal = dims[0] * dims[1]
+    horizontal = dims[0]
     shelves.append({
         'dist' : dist,
         'horizontal' : horizontal,
@@ -62,7 +62,7 @@ for i in range(len(decisions)):
     assert len(decisions[i]) == len(items)
     shelf_length_expr = decisions[i][0] * items[0]['horizontal']    
     for j in range(len(decisions[i]) - 1):
-        shelf_length_expr += decisions[i][j + 1] * items[j + 1]['horizontal']
+        shelf_length_expr = shelf_length_expr + decisions[i][j + 1] * items[j + 1]['horizontal']
     m.addConstr(shelf_length_expr <= shelves[i]['horizontal'])
 
 # Items can only go into one spot

### 2018-11-30 solver.py
1D + 3x shelf stacking works, also split big boi into 2

@@ -1,6 +1,7 @@
 #!/usr/local/bin/python3
 from gurobipy import *
 
+STACKING = 3
 subs = {
     'Chassis' : 0,
     'Arm' : 1,
@@ -33,11 +34,12 @@ for line in f:
     dims = [float(x) for x in substrs[1].split('x')]
     component = int(substrs[2])
     horizontal = dims[0]
-    shelves.append({
-        'dist' : dist,
-        'horizontal' : horizontal,
-        'comp' : component
-    })
+    for _ in range(STACKING):
+        shelves.append({
+            'dist' : dist,
+            'horizontal' : horizontal,
+            'comp' : component
+        })
 f.close()
 
 m = Model()
@@ -92,8 +94,11 @@ m.setObjective(obj, GRB.MINIMIZE)
 m.update()
 m.optimize()
 
-for shelf in range(len(shelves)):
+real_shelves = int(len(shelves) / STACKING)
+for shelf in range(real_shelves):
     print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf]['comp'], shelves[shelf]['dist']))
-    names = [items[x]['name'] for x in range(len(decisions[shelf])) if decisions[shelf][x].X > 0]
-    for item in names:
-        print('\t' + item)
+    for i in range(STACKING):
+        split_shelf = shelf + real_shelves * i
+        names = [items[x]['name'] for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0]
+        for item in names:
+            print('\t' + item)

### 2018-11-30 paper.tex
removed todo
added link to code
made lines in tex file a decent size
added simplifying assumption

@@
 
-\textbf{\color{red} TODO: More related work}
+%\textbf{\color{red} TODO: More related work}
 
-\section{Assumptions}
+\section{Simplifying Assumptions}
 Most items in the robotics closet are in boxes. As a result, we assume that all
@@
 \par
-We also assumed that certain parts of the robotics closet are not to be moved.
-For example, the shelf containing aluminum brackets and blocks for machining was excluded from the model entirely.
-This is due to the cumbersome nature of moving hundreds of unboxed chunks of metal, and due to opposition to its transportation by team members who frequently use it.
-The food pantry portion as well as some non-food items that made their way into it was similarly excluded after brief deliberation.
-Excluding parts of the closet from the model does not reduce the validity of the remaining optimization since the access to other closets is unaffected by the contents of these.
+We also assumed that certain parts of the robotics closet are not to be moved. For
+example, the shelf containing aluminum brackets and blocks for machining was excluded
+from the model entirely. This is due to the cumbersome nature of moving hundreds of
+unboxed chunks of metal, and due to opposition to its transportation by team members
+who frequently use it. The food pantry portion as well as some non-food items that
+made their way into it was similarly excluded after brief deliberation. Excluding
+parts of the closet from the model does not reduce the validity of the remaining
+optimization since the access to other closets is unaffected by the contents of these.
 \par
-Another simplifying assumption we made is that all drawers have one unit of depth.
-In other words, we cannot insert items one behind another.
-This is a valid assumption to make because having to pull an item from behind another would drastically reduce the retrieval time of both items, undoing much of the benefits of our optimization.
-This can be adjusted to be a soft constraint (penalize heavily for items that are one behind another) if the model is infeasible without this change.
-In the meantime, we are reasonably confident that disallowing multiple units of depth is the best approach keeping in mind our ultimate goal of convenience.
-
+Another simplifying assumption we made is that all shelves have one unit of depth.
+In other words, we cannot insert items one behind another. This is a valid assumption
+to make because having to pull an item from behind another would drastically reduce the
+retrieval time of both items, undoing much of the benefits of our optimization. This
+can be adjusted to be a soft constraint (penalize heavily for items that are one
+behind another) if the model is infeasible without this change. In the meantime, we
+are reasonably confident that disallowing multiple units of depth is the best
+approach keeping in mind our ultimate goal of convenience.
+\par
+Lastly, we assumed that there can be on average 3 items in the same 1-D linear
+segment. We arrived at this assumption by noticing that the fast majority of
+items are in the same type of box, which are 21 cm wide. Since shelf widths
+range from 74 cm to 91 cm, 3 boxes fit comfortably on three shelves. This
+also has the advantage of providing padding to the items to ease retrieval. 
 \section{Model}
@@
 \end{thebibliography}
+Source code can be found at: https://github.com/save-buffer/math381
 \end{document}

### 2018-11-30 paper.tex
Fixed a couple bugs, updated paper

@@
 \par
-Another simplifying assumption we made is that all shelves have one unit of depth.
-In other words, we cannot insert items one behind another. This is a valid assumption
-to make because having to pull an item from behind another would drastically reduce the
-retrieval time of both items, undoing much of the benefits of our optimization. This
-can be adjusted to be a soft constraint (penalize heavily for items that are one
-behind another) if the model is infeasible without this change. In the meantime, we
-are reasonably confident that disallowing multiple units of depth is the best
-approach keeping in mind our ultimate goal of convenience.
+We also assumed that there can be on average 3 items in the same 1-D linear
+segment. This means that by using some combination of placing items behind
+and above other items, we can fit 3 items in that segment. This is a rough
+estimate that we came to empirically. This makes sense because some shelves are
+very deep, and all shelves fit at least 2 of the boxes vertically, since
+the boxes are 12.5 cm tall, and all shelves are taller than 25 cm. 
 \par
-Lastly, we assumed that there can be on average 3 items in the same 1-D linear
-segment. We arrived at this assumption by noticing that the fast majority of
-items are in the same type of box, which are 21 cm wide. Since shelf widths
-range from 74 cm to 91 cm, 3 boxes fit comfortably on three shelves. This
-also has the advantage of providing padding to the items to ease retrieval. 
+The previous assumption let us assume for our model is shelves have one unit of depth
+and one unit of height. In other words, the model does not have to take into account
+insertion of items one behind another. To model height, we make use of the previous
+assumption to ``duplicate'' shelves, defining the duplicates to be above the original
+one. We can model depth in the same way. 
 \section{Model}
 We collected data from the robotics closet by measuring each item and shelf. Each
-shelf $s$ is represented as an ordered triple $(d, a, c)$, where $d$ is the
-distance from the door in ``shelf-lengths'', $a$ is the area of the shelf, and
-$c$ is the connected components to which the self belongs.
+shelf $s$ is represented as an ordered triple $(d, l, c)$, where $d$ is the
+distance from the door in ``shelf-lengths'', $l$ is the length of the shelf, and
+$c$ is the connected component to which the self belongs.
 \par
-Each item is represented with an ordered triple $(a, p, s)$, where $a$ is the area
+Each item is represented with an ordered triple $(l, p, s)$, where $l$ is the length
 of the item, $p$ is the probability that the item is selected, and $s$ is the item's
-subsystem. Notice that we represent each item as a 2-dimensional area. This is valid
-because we assumed that each shelf had a single unit of depth. As a preprocessing step,
-we choose to minimize the area. However, we cannot rotate always the item into a
-horizontal orientation. Therefore, $h$ is constant. For an item $i$ with length $l_i$,
-width $w_i$, and height $h_i$, its area $a_i$ is given by 
-$$a_i = \min(l_i, w_i) \cdot h_i$$
+subsystem. Notice that we represent each item as a 1-dimensional length. This is valid
+because we assumed that each shelf had a single unit of depth and a single
+unit of height. As a preprocessing step, minimize the length. Since we cannot always
+rotate an item into a horizontal orientation, for an item with dimensions $a \times b$
+the item's 1-dimensional length is given by 
+$$l = \min(a, b)$$
 \par
-Let there be $n$ shelves and $m$ items, $k$ subsystems, and $l$ is the number of
-connected components. Our decision variables lie in two matrices
+Let there be $n_0$ shelves and $m$ items, $k$ subsystems, and $n_c$ be the number of
+connected components. In order to simulate stacking and placing behind, we
+multiply the number of shelves by our assumed average number of items per
+1-dimensional block. In our model, we chose 3 as our constant. Thus,
+the total number of shelves in the model is $n = 3n_0$. 
+Our decision variables lie in two matrices
 $$W = (w_{ij}), 1 \leq i \leq n, 1 \leq j \leq m$$
@@
 $1$ if subsystem $j$ lies in connected component $i$ and $0$ otherwise. 
-$C$ is a $l \times k$ matrix because there are l connected components and k subsystems. \\
-Note about notation: $a^i_k$ indicates the area of item $k$ while $a^s_k$ indicates the
-area of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
+$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. \\
+Note about notation: $l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
+length of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
 $x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 
@@
 \begin{enumerate}
-\item $\sum_{j = 1}^{m}w_{ij}a^i_j \leq w^s_i, 1 \leq i \leq n$.
+\item $\sum_{j = 1}^{m}w_{ij}l^i_j \leq l^s_i, 1 \leq i \leq n$.
 \item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
@@
 \begin{enumerate}
-\item The sum of all of the items on a given shelf must be less than or equal to
-  the maximum area that the shelf can support. We multiply by $w_{ji}$ so that
+\item The sum the lengths of all of the items on a given shelf must be less than or equal to
+  the maximum length that the shelf can support. We multiply by $w_{ji}$ so that
   items not included on the shelf are not counted.
@@
 \begin{itemize}
-\item Dr. Sara Billey for providing us with guidance throughout the project,
+\item Prof. Sara Billey for providing us with guidance throughout the project,
 \item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,

### 2018-11-30 solver.py

@@ -2,6 +2,7 @@
 from gurobipy import *
 
 STACKING = 3
+NUM_COMPONENTS = 4
 subs = {
     'Chassis' : 0,
     'Arm' : 1,
@@ -52,7 +53,7 @@ for shelf in shelves:
         decisions[-1].append(m.addVar(vtype=GRB.BINARY))
 
 connected_comp_decisions = []
-for i in range(3):
+for i in range(NUM_COMPONENTS):
     connected_comp_decisions.append([])
     for j in range(len(subs)):
         connected_comp_decisions[-1].append(m.addVar(vtype=GRB.BINARY))
@@ -82,7 +83,7 @@ for sub in range(len(subs)):
 # Items from the same subsystem must be in the same connected component
 for sub in range(len(subs)):
     item_indices = [i for i in range(len(items)) if items[i]['sub'] == sub]
-    for component in range(3):
+    for component in range(NUM_COMPONENTS):
         shelf_indices = [i for i in range(len(shelves)) if shelves[i]['comp'] == component]
         expr = sum([sum([decisions[j][i] for j in shelf_indices]) for i in item_indices])
         m.addConstr(expr == (len(item_indices) * connected_comp_decisions[component][sub]))
@@ -96,9 +97,9 @@ m.optimize()
 
 real_shelves = int(len(shelves) / STACKING)
 for shelf in range(real_shelves):
-    print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf]['comp'], shelves[shelf]['dist']))
+    print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf * STACKING]['comp'], shelves[shelf * STACKING]['dist']))
     for i in range(STACKING):
-        split_shelf = shelf + real_shelves * i
+        split_shelf = shelf * STACKING + i
         names = [items[x]['name'] for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0]
         for item in names:
             print('\t' + item)

### 2018-12-03 paper.tex
symbol fixes

@@
 We collected data from the robotics closet by measuring each item and shelf. Each
-shelf $s$ is represented as an ordered triple $(d, l, c)$, where $d$ is the
-distance from the door in ``shelf-lengths'', $l$ is the length of the shelf, and
+shelf $s$ is represented as an ordered triple $(d, L, c)$, where $d$ is the
+distance from the door in ``shelf-lengths'', $L$ is the length of the shelf, and
 $c$ is the connected component to which the self belongs.
@@
 $C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. \\
-Note about notation: $l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
+Note about notation: ($l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
 length of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
-$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. 
+$x$, $p_x$ and $s_x$ represent the item's probability and subsystem respectively. Let
+there be $n_0$ shelves and $m$ items, $k$ subsystems, and $n_c$ be the number of 
+connected components.)
 \par
 The model is subject to the following constraints:
+\\
 \begin{enumerate}

### 2018-12-05 solver.py
Added output file

@@ -96,10 +96,16 @@ m.update()
 m.optimize()
 
 real_shelves = int(len(shelves) / STACKING)
+output = open('output.tsv', 'w')
 for shelf in range(real_shelves):
     print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf * STACKING]['comp'], shelves[shelf * STACKING]['dist']))
+    to_print = '%d\t%d\t' % (shelf, shelves[shelf * STACKING]['dist'])
+    names = []
     for i in range(STACKING):
         split_shelf = shelf * STACKING + i
-        names = [items[x]['name'] for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0]
-        for item in names:
-            print('\t' + item)
+        names += ([{'name' : items[x]['name'], 'prob' : items[x]['prob']} for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0])
+    names = sorted(names, key=lambda x : x['prob'], reverse=True)
+    for item in names:
+        print('\t' + item['name'])
+        to_print += item['name'] + '\t'
+    output.write(to_print + '\n')

### 2018-12-05 paper.tex
symbol fixes. tried to lower usage of i, j, l

@@
 We collected data from the robotics closet by measuring each item and shelf. Each
-shelf $s$ is represented as an ordered triple $(d, L, c)$, where $d$ is the
-distance from the door in ``shelf-lengths'', $L$ is the length of the shelf, and
+shelf $s$ is represented as an ordered triple $(d, L^{shelf}, c)$, where $d$ is the
+distance from the door in ``shelf-lengths'', $L^{shelf}$ is the length of the shelf, and
 $c$ is the connected component to which the self belongs.
 \par
-Each item is represented with an ordered triple $(l, p, s)$, where $l$ is the length
+Each item is represented with an ordered triple $(L^{item}, p, s)$, where $L^{item}$ is the length
 of the item, $p$ is the probability that the item is selected, and $s$ is the item's
@@
 because we assumed that each shelf had a single unit of depth and a single
-unit of height. As a preprocessing step, minimize the length. Since we cannot always
+unit of height. As a pre-processing step, minimize the length. Since we cannot always
 rotate an item into a horizontal orientation, for an item with dimensions $a \times b$
 the item's 1-dimensional length is given by 
-$$l = \min(a, b)$$
+$$L^{item} = \min(a, b)$$
 \par
@@
 $1$ if subsystem $j$ lies in connected component $i$ and $0$ otherwise. 
-$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. \\
+$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. 
 Note about notation: ($l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
@@
 The model is subject to the following constraints:
-\\
 \begin{enumerate}
-\item $\sum_{j = 1}^{m}w_{ij}l^i_j \leq l^s_i, 1 \leq i \leq n$.
-\item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
-\item $\sum_{j = 1}^{l}c_{ji} = 1, 1 \leq i \leq k$.
+\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n_0$ ($n_0 = $ number of shelves).
+\item $\sum_{i = 1}^{n}w_{ij} = 1, $ for every $1 \leq j \leq m$ ($m = $ number of items).
+\item $\sum_{j = 1}^{l}c_{ji} = 1, $ for every $1 \leq i \leq k$.
 \item Let $K$ be the set of indices of items belonging to subsystem $i$. Let
@@
   traverse the whole column and ensure its sum is exactly $1$. Notice that if
-  we had put $\leq 1$, the constraint would have been invalid because then
-  no items would have been included. Thus, this constraint implicitly enforces
+  we had put $\leq 1$, the constraint would be invalid because then
+  no items could have been included. Thus, this constraint implicitly enforces
   the constraint that every item be included.

### 2018-12-05 solver.py
Print in subshelves

@@ -99,13 +99,13 @@ real_shelves = int(len(shelves) / STACKING)
 output = open('output.tsv', 'w')
 for shelf in range(real_shelves):
     print('Shelf %d (connected component %d, distance %d):' % (shelf, shelves[shelf * STACKING]['comp'], shelves[shelf * STACKING]['dist']))
-    to_print = '%d\t%d\t' % (shelf, shelves[shelf * STACKING]['dist'])
-    names = []
     for i in range(STACKING):
+        names = []
+        to_print = '%d\t%d\t' % (shelf, shelves[shelf * STACKING]['dist'])
         split_shelf = shelf * STACKING + i
         names += ([{'name' : items[x]['name'], 'prob' : items[x]['prob']} for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0])
-    names = sorted(names, key=lambda x : x['prob'], reverse=True)
-    for item in names:
-        print('\t' + item['name'])
-        to_print += item['name'] + '\t'
-    output.write(to_print + '\n')
+        names = sorted(names, key=lambda x : x['prob'], reverse=True)
+        for item in names:
+            print('\t' + item['name'])
+            to_print += item['name'] + '\t'
+        output.write(to_print + '\n')

### 2018-12-05 solver.py
output dimensions of items

@@ -22,6 +22,7 @@ for line in f:
     items.append({
         'name' : substrs[0],
         'horizontal' : horizontal,
+        'vertical' : dims[2],
         'prob' : prob,
         'sub'  : subs[substrs[2]]
     })
@@ -103,9 +104,9 @@ for shelf in range(real_shelves):
         names = []
         to_print = '%d\t%d\t' % (shelf, shelves[shelf * STACKING]['dist'])
         split_shelf = shelf * STACKING + i
-        names += ([{'name' : items[x]['name'], 'prob' : items[x]['prob']} for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0])
+        names += ([items[x] for x in range(len(decisions[split_shelf])) if decisions[split_shelf][x].X > 0])
         names = sorted(names, key=lambda x : x['prob'], reverse=True)
         for item in names:
             print('\t' + item['name'])
-            to_print += item['name'] + '\t'
+            to_print += item['name'] + '\t' + str(item['horizontal']) + '\t' + str(item['vertical']) + '\t'
         output.write(to_print + '\n')

### 2018-12-05 visualizer/js.js
finalize visualizer

@@ -1,8 +1,118 @@
 window.onload = ()=>{
 	let c = document.getElementById("c"), g = c.getContext("2d");
 	g.fillStyle = "black";
-	
-	const SHELVES = [
-		{width: 12, height: 8}
-	];
+
+    var shelves;
+    let SCALE = 2.6,
+        COLORS = ["128, 255, 255", "255, 128, 255", "255, 255, 128", "255, 168, 48"],
+        ITEM_FILLSTYLE = "rgba(0,0,0,0.5)",
+        ALPHA = 0.24;
+    
+    function bindFileInput(id, f) {
+        document.getElementById(id).addEventListener("change", (e)=>{
+            let file = e.target.files[0];
+            if (!file) return;
+            let reader = new FileReader();
+            reader.onload = function(e) {
+                contents = e.target.result;
+                f(contents);
+            };
+            reader.readAsText(file);
+        });
+    }
+    bindFileInput("shelves", prepShelves);
+    bindFileInput("model", prepItems);
+
+
+    function prepItems(content) {
+        let lines = content.split("\n").map(line => line.split("\t"));
+        for(let idx = 0; idx < 42; idx++) {
+            let line = lines[idx];
+            if(line.length <= 3) continue;
+            let items = [];
+            for(let i = 2; i < line.length - 1; i+=3) {
+                items.push({width: parseInt(line[i+1]), height: parseInt(line[i+2])});
+            }
+            let shelf = shelves[parseInt(line[0])];
+            shelf.items = shelf.items || [];
+            shelf.items.push(items);
+        }
+        draw();
+    }
+
+    function prepShelves(content) {
+        let lines = content.split("\n");
+        const keys = ["dist", "width", "height", "component"];
+        shelves = lines.map(line => line.replace(" x ", "\t").split("\t"));
+        //shelves = lines.map(line => line.replace(" x ", "\t").split("\t").reduce((acc, el, i)=>{acc[keys[i]]=el;return acc;}));
+        let shelfObjects = [];
+        for(shelf in shelves) {
+            shelf = shelves[shelf];
+            shelfObjects.push({
+                dist: shelf[0],
+                width: parseInt(shelf[1]),
+                height: parseInt(shelf[2]),
+                component: parseInt(shelf[3])
+            });
+        }
+        shelves = shelfObjects;
+    }
+
+    function line(x, y, x2, y2) {
+        g.beginPath();
[…]

### 2018-12-11 visualizer/js.js
consolidate big shelf that's not used anyway, label shelves in visualizer, create closet2.png with shelves labeled on the image

@@ -3,10 +3,11 @@ window.onload = ()=>{
 	g.fillStyle = "black";
 
     var shelves;
-    let SCALE = 2.6,
+    let SCALE = 2.8,
         COLORS = ["128, 255, 255", "255, 128, 255", "255, 255, 128", "255, 168, 48"],
         ITEM_FILLSTYLE = "rgba(0,0,0,0.5)",
-        ALPHA = 0.24;
+        ALPHA = 0.24,
+        SHELF_COUNTS = [4, 5, 3, 1];
     
     function bindFileInput(id, f) {
         document.getElementById(id).addEventListener("change", (e)=>{
@@ -27,13 +28,13 @@ window.onload = ()=>{
     function prepItems(content) {
         let lines = content.split("\n").map(line => line.split("\t"));
         for(let idx = 0; idx < 42; idx++) {
-            let line = lines[idx];
+            let line = lines[idx >= 3 ? idx - 3: idx];
             if(line.length <= 3) continue;
             let items = [];
             for(let i = 2; i < line.length - 1; i+=3) {
                 items.push({width: parseInt(line[i+1]), height: parseInt(line[i+2])});
             }
-            let shelf = shelves[parseInt(line[0])];
+            let shelf = shelves[parseInt(line[0] - 1)];
             shelf.items = shelf.items || [];
             shelf.items.push(items);
         }
@@ -44,16 +45,19 @@ window.onload = ()=>{
         let lines = content.split("\n");
         const keys = ["dist", "width", "height", "component"];
         shelves = lines.map(line => line.replace(" x ", "\t").split("\t"));
+        shelves.shift();
         //shelves = lines.map(line => line.replace(" x ", "\t").split("\t").reduce((acc, el, i)=>{acc[keys[i]]=el;return acc;}));
         let shelfObjects = [];
-        for(shelf in shelves) {
-            shelf = shelves[shelf];
-            shelfObjects.push({
+        for(idx in shelves) {
+            shelf = shelves[idx];
+            let obj = {
                 dist: shelf[0],
                 width: parseInt(shelf[1]),
                 height: parseInt(shelf[2]),
                 component: parseInt(shelf[3])
-            });
+            };
+            if(idx == 0) obj.height *= 2;
+            shelfObjects.push(obj);
         }
         shelves = shelfObjects;
     }
@@ -85,7 +89,7 @@ window.onload = ()=>{
 
     function draw() {
[…]

### 2018-12-11 paper.tex
fix small JS bug, add abstract, regenerate image

@@
 \maketitle
+\begin{abstract}
+The present organization of the closet space allocated to the University of Washington's Husky Robotics team leaves much to be improved.
+With carefully selected simplifying assumptions, we propose a linear programming solution to the closet organization problem.
+Although the general packing problem is NP-hard, this application allows for a relatively reasonable simplification to one dimensional space with duplicating each shelf to represent multiple layers of items depth-wise and height-wise.
+The items are optimized for how distant the shelf they are put into is, and futher arranged within each shelf by probability of access.
+We used the Gurobi python package to solve the MILP problem, and a custom HTML5/JS script to visualize the solution output by Gurobi.
+The result is an organization scheme that, when implemented, can be expected to improve the average time spent by each robotics team member when visiting the closet.
+\end{abstract}
 \pagebreak

### 2018-12-11 visualizer/js.js

@@ -28,7 +28,7 @@ window.onload = ()=>{
     function prepItems(content) {
         let lines = content.split("\n").map(line => line.split("\t"));
         for(let idx = 0; idx < 42; idx++) {
-            let line = lines[idx >= 3 ? idx - 3: idx];
+            let line = lines[idx];
             if(line.length <= 3) continue;
             let items = [];
             for(let i = 2; i < line.length - 1; i+=3) {

### 2018-12-11 paper.tex
switch to labeled closet
finalize some things, including removing whitespace from image

@@
 \usepackage{xcolor}
+\usepackage{geometry}
+\usepackage{titling}
 \graphicspath{{.}}
@@
 \newtheorem*{nthm}{Theorem}
+\setlength{\droptitle}{-10em}
 \title{Optimizing the Robotics Closet}
@@
 We used the Gurobi python package to solve the MILP problem, and a custom HTML5/JS script to visualize the solution output by Gurobi.
-The result is an organization scheme that, when implemented, can be expected to improve the average time spent by each robotics team member when visiting the closet.
+The result is an organization scheme that, when implemented, can be expected to improve the average time spent when visiting the closet.
 \end{abstract}
+\begin{center}
+\includegraphics[scale=0.15]{rover.png}
+\end{center}
 \pagebreak
@@
 same subsystem are in the same connected component on the shelves.
+By minimizing the time spent in the closet searching for items, and being able to find multiple items they need in a similar place, the team will have more time to spend building the robot each meeting.
 \par
@@
 the middle of the room on a big cart. Behind it is the robotic arm and the
-vscience station. In the back are the sheet metal, various metallic cylinders,
+science station. In the back are various metallic cylinders, sheet metal,
 wood, and rolls of carbon fiber. By examining the frequencies of retrieval
@@
 a better layout of the closet.
-
+\pagebreak
 \begin{center}
-  \includegraphics[scale=0.15]{closet.jpg} \\
-  The robotics closet before optimization. 
+  \includegraphics[scale=0.7]{closet2.png} \\
+  The robotics closet before optimization. Shelves are labeled to match the solution visualization.
 \end{center}
@@
 \section{Simplifying Assumptions}
+\par
 Most items in the robotics closet are in boxes. As a result, we assume that all
@@
 parts of the closet from the model does not reduce the validity of the remaining
-optimization since the access to other closets is unaffected by the contents of these.
+optimization since those areas do not intrude on the access to the shelves the model does consider.
 \par
@@
   can be in exactly one connected component. Similarly to constraint 2, summing
-  this and ensuring that the sum is 1 enforces the idea that every subsystem is
+  the column and ensuring that the sum is 1 enforces the idea that every subsystem is
   included.
 \item The intuition behind this constraint is that either all items belonging
-  to a subsystem are in the same connected component, or none are. Thus, we
+  to a subsystem are in a given connected component, or none are. Thus, we
   use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not. 
@@
 drawers to collect dust.
+Unfortunately, the difficulty of making the model work correctly with the 1D simplification presently prevented us from tackling it, but with more time to invest, this could be fine tuned, or the model could be switched to 2D or 3D.
 
@@
 Source code can be found at: https://github.com/save-buffer/math381
+
+\pagebreak
+\newgeometry{left=3cm,right=3cm,top=3cm,bottom=3cm}
+\section{Appendix: Solution Visualization}
+\includegraphics[scale=0.40,angle=90]{image.png}
 \end{document}

### 2018-12-12 paper.tex
turned it in!

@@
 $C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. 
-Note about notation: ($l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
+Note about notation: ($L^{item}_k$ indicates the length of item $k$ while $L^{shelf}_k$ indicates the
 length of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item
@@
 \begin{enumerate}
-\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n_0$ ($n_0 = $ number of shelves).
+\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n$ ($n = $ number of shelves, including stacking).
 \item $\sum_{i = 1}^{n}w_{ij} = 1, $ for every $1 \leq j \leq m$ ($m = $ number of items).
@@
 as are NVIDIA Jetsons and other closely related items. This validates that the
-connected components constraint is being considered.
+connected components constraint is being considered. A visualization of our
+result is included in the appendix.
 
@@
 it is illogical to stuff some shelves to the last inch while leaving whole
-drawers to collect dust.
-Unfortunately, the difficulty of making the model work correctly with the 1D simplification presently prevented us from tackling it, but with more time to invest, this could be fine tuned, or the model could be switched to 2D or 3D.
+drawers to collect dust. Unfortunately, the difficulty of making the model
+work correctly with the 1D simplification presently prevented us from tackling
+it, but with more time to invest, this could be fine tuned, or the model
+could be switched to 2D or 3D.
 
@@
 
+\pagebreak
 \section{References}
@@
 \section{Appendix: Solution Visualization}
-\includegraphics[scale=0.40,angle=90]{image.png}
+\includegraphics[scale=0.40,angle=90]{visualizer/image.png}
 \end{document}
